### 2018-03-12 paper/3-compute.tex
Add description of track

\noindent
The task corresponding to the cell \cmd{B1} statically depends on \cmd{C1} and
dynamically depends on either \cmd{A1} or \cmd{A2}. We can express this using
our compute abstraction as follows\footnote{The spreadsheet example that uses
the \hs{INDIRECT} function can be expressed as well: simply replace the last
line of the \hs{select} function with \hs{fetch ("A" ++ show c1)}.}:

@@

% Note that this presentation of build tasks makes dynamic dependencies
% immediately recognisable: we need to examine the actual value \hs{c1} by
% extracting it from the computational context using \hs{Monad}'s bind statement
% \hs{c1 <- fetch}

Now we need a combination of \hs{Const} and \hs{Identity}, which is the
\hs{Writer} monad!

>>>>

\noindent
The task corresponding to the cell \cmd{B1} statically depends on \cmd{C1} and
dynamically depends on either \cmd{A1} or \cmd{A2}. We can express this using
our compute abstraction as follows\footnote{The spreadsheet example that uses
the \hs{INDIRECT} function can be expressed very similarly: simply replace the
last line of the \hs{select} function with \hs{fetch ("A" ++ show c1)}.}:

@@

\noindent
In the above execution $\cmd{C1} \neq 1$, hence the \hs{else} branch is taken.
To extract the dependencies of \hs{select} we introduce the function \hs{track}:
a combination of \hs{execute} and \hs{dependencies} that takes the store~\store
as input and computes both the resulting value and the list of its dependencies:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
import Control.Monad.Writer
\end{minted}
\vspace{0.5mm}
\begin{minted}[xleftmargin=10pt]{haskell}
track :: Compute Monad k v -> (k -> v) -> k -> Maybe (v, [k])
track compute store = fmap runWriter . compute (\k -> writer (store k, [k]))
\end{minted}
\vspace{1mm}

\noindent
The implementation uses the \hs{Writer} monad (\S\ref{sec-appendix-transformers}):
we feed \hs{fetch k = writer (store k, [k])} to the compute, which in addition
to fetching a value from the store, tracks the corresponding key. We can use
\hs{track} to track both applicative and monadic compute:

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ store key = if key == "A1" then 10 else 20
@\ghci@ track add store "B1"
Just (30,["A1","A2"])
\end{minted}
\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
@\ghci@ track select store "B1"
Just (20,["C1","A2"])
\end{minted}
\vspace{1mm}
